### 2002-08-26 dialoguesisters/en/DialogueSisters.tex
no message

\item[(4)] One finds details to this RSA-procedure in the following book: {\small
  NEAL KOBLITZ}, {\em A Course in Number Theory and Cryptography\/},
second edition, chapter IV, paragraph 2; Springer-Verlag, 1994. \\
\end{itemize}
\[\]
\hrulefill
\[\]
\[\]
{\em Note of the translator:} \\
I want to thank Mr Richard Christensen for his review of this translation.
\\[1ex]
With CrypTool version 1.3 and higher it is easy to comprehend this variant of the RSA encryption scheme by using 
the following steps: \\
menu {\bf Indiv. Procedures / RSA Demonstration / RSA Cryptosystem\dots}. \\
Within the following dialog box {\bf The RSA Cryptosystem} choose the second option -- knowing only public parameters -- and factorize N. The given 
two code numbers (e.g. 51, 3) of Bianca and Doris are N and e. The algorithms behind can be switched to this 
special variant by hitting the button \textbf{Options for alphabet and number system\dots}. \\
In the following dialog 
box {\bf Options for RSA Encryption} select \textbf{Dialogue of the Sisters} and limit the alphabet to exactly 26 
letters (A, B, ..., Y, Z).

>>>>

\item[(4)] One finds details to this RSA-procedure in the following book: {\small
  NEAL KOBLITZ}, {\em A Course in Number Theory and Cryptography\/},
second edition, chapter IV, paragraph 2; Springer, 1994. \\
\end{itemize}
\[\]
\hrulefill
\[\]
\[\]
{\em Note of the translator:} \\
I want to thank Mr Richard Christensen for his review of this translation.
\\[1ex]
With CrypTool version 1.3 and higher it is easy to comprehend this variant of the RSA encryption scheme by using 
the following steps: \\
menu {\bf Indiv. Procedures / RSA Demonstration / RSA Cryptosystem\dots}. \\
Within the following dialog box {\bf The RSA Cryptosystem} choose the second option -- knowing only public parameters -- and factorize N. The given 
two code numbers (e.g. 51, 3) of Bianca and Doris are N and e. The algorithms behind can be switched to this 
special variant by hitting the button \textbf{Options for alphabet and number system\dots}. \\
In the following dialog 
box {\bf Options for RSA Encryption} select \textbf{Dialogue of the Sisters} and limit the alphabet to exactly 26 
letters (A, B, ..., Y, Z).
